Unit tests

### 2018-04-02 Tests.Rmd
adding tests for mydispersal.R

>>>>

# Tests for retd() function from ExtremeTailDep.R
<!--DCR to add this section-->

# Tests for mydispersal.R

**Test for `Dispersal_mat` function**

```{r test_for_Dispersal_mat}
source("mydispersal.R")
set.seed(101)
D1<-Dispersal_mat(numlocs=3,d=0.4,disp_everywhere=F)
D1  #matrix for dispersion between nearest neighbours in a linear chain model
D2<-Dispersal_mat(numlocs=3,d=0.4,disp_everywhere=T) 
D2  #matrix for dispersion between any nodes in a linear chain model
if((isSymmetric.matrix(D1)==F) & (isSymmetric.matrix(D2)==T)){print("Dispersal_mat : passed")} 
```

**Test for `popsim_ml_D`  and `extrisk` function**
<!-- I assume here that retd() function is already checked and passed the test
#-------Args--------------------------------------------------
#p0       A length numlocs vector holding initial populations
#ns       An numsims by numlocs by numsteps array of the epsilons, 
#           where numsteps is the number of time steps you want
#
#--------Output------------------------------------------------------
#A numsims by numlocs by numsteps+1 array of populations
#----------------------------------------------------------------------
popsim_ml_D<-function(p0,ns,D,r,K)
-->
```{r test_for_popsim_ml_D, echo=T}
source("mydispersal.R")
set.seed(101)
numsteps<-15
numsims<-4
numlocs<-3

ns1<-retd(n=numsteps*numsims,d=numlocs,rl=1) # output from ExtremeTailDep.R : 
#                                                      a righttail dep matrix(numpoints by numlocs,     
#                                                      numpoints=numsteps*numsims)
dim(ns1)
ns1<-array(ns1,c(numsteps,numsims,numlocs))# convert to an array (numsteps by numsims by numlocs)
if(all(dim(ns1)==c(numsteps,numsims,numlocs))==T){print("passed")}
ns1<-aperm(ns1,c(2,3,1)) # convert to an array (numsims by numlocs by numsteps)
if(all(dim(ns1)==c(numsims,numlocs,numsteps))==T){print("passed")}

D<-D1
r<-0.5
K<-10
res<-popsim_ml_D(p0=rep(K,numlocs),ns=ns1,D=D1,r=r,K=K)
res[,,1]
res[,,2]
res[,,numsteps+1]
if(all(dim(res)==c(numsims,numlocs,numsteps+1))==T){print("popsim_ml_D : passed")}

# test for extrisk function
totpop<-apply(FUN=sum,X=res,MARGIN=c(1,3))
totpop # numsims by numsteps+1 matrix
if(all(totpop[,1]==(numlocs*K))==T){print("passed")}
ext<-(apply(FUN=sum,X=(totpop==0),MARGIN=2)/dim(res)[1])
ext
if(length(ext)==numsteps+1){print("passed")}

ans<-extrisk(sims=res)
if(all(ext==ans)==T){print("extrisk : passed")}
```
